\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{fontspec}
\setmainfont[Path=/usr/share/fonts/TTF/,
BoldItalicFont=timesbi.ttf,
BoldFont      =timesbd.ttf,
ItalicFont    =timesi.ttf]{times.ttf}

\renewcommand*\contentsname{TABLE OF CONTENTS}
\begin{document}
\begin{titlepage}
\begin{center}
    {\Large\bfseries INFORMATICS INSTITUTE OF TECHNOLOGY \\ in collaboration with \\
    the University of Westminster, UK\\}
\vspace{1cm}
{\Large \bfseries BEng (Hons) DEGREE PROGRAMME in \\ Software Engineering\\}
\vspace{2.5cm}
{\Large\bfseries REPORT ON INDUSTRIAL PLACEMENT \\ of \\ Muiz Uvais\\}
\vspace{2cm}
{\Large in relation to the work carried out at \\ iTelaSoft \\ 69 Old Kottawa Rd, Nugegoda 10250 \\ 2020\\}

\end{center}

\end{titlepage}

\section*{Acknowledgement}
I would like to sincerely thank and acknowledge iTelaSoft,
and it's management for giving me the opportunity for giving 
me the opportunity for me to do my Industrial Placement.
\newline
\newline
I would also like to thank the my supervisors
Manoj, and Deepan for guiding me through the industrial placement. \newline \newline 
Last but not least
I also would like to thank my colleagues at team EFFI who helped me out when I got stuck or was new to
certain areas.
\newpage

\tableofcontents

\section*{ILLUSTRATIONS} 
\section*{ABBREVIATIONS}
{\large IIT -- (The) Informatics Institute of Technology\\}
\newline
{\large SE -- Software Engineering\\}
\newline
{\large ITS -- iTelaSoft\\}
\newline
{\large UoW -- University of Westminster\\}
\newline
{\large IP -- Industrial Placement}
\newpage


\section{Introduction}
An Industrial Placement is an experience where the intention is to prepare the student for their
future employment, therefore the industrial placement is an integral part of the process of 
entering the SE industry. As an SE student I feel extremely fortunate that IIT in collaboration with
the UoW has given this path for students enrolled in this course.\\
\newline
While working at ITS I was able to gain experience working in a lot of areas. These areas included 
front-end as well as a bit of work in the back-end. Although I did more work in the front-end, I have
also gained an insight into back-end. I feel that I have benefited greatly from my exposure to those 
technologies. However, I have also gained exposure to soft skills which has been equally beneficial
to me. Working for a company like ITS I have been able to learn to deal with tough situations
that would usually come up in the industry. Therefore I can safely conclude that the IP will play
an foundational role in my career.\\
\newline
At work I received a lot of support from my team members. I worked in the web development field which
is the main scope of the company, most of my co-workers were well experienced, and extremely helpful
to me.\\
\newline
I started my placement on the 02st of July 2019, and completed it on the 01st of July 2020. While 
there were obstacles I faced it was an important experience that I will always remember.
\newpage

\section{Company Profile}
iTelaSoft is a premier IT company, which is located at 69 Old Kottawa Rd, Nugegoda 10250. It's
mission statement is 

\end{document}
